---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

# volleyxml

[![Travis-CI Build Status](https://travis-ci.org/raymondben/volleyxml.svg?branch=master)](https://travis-ci.org/raymondben/volleyxml)

An R package for reading volleyball scouting files in the [hudl](https://www.hudl.com/sports/volleyball) XML format. Files in this format can be exported from scouting apps including [iStatVball 2](http://www.istatvball.com/), [SoloStats Live](https://www.solostatslive.com/solostats-live.html), and others. (This R package is not affiliated with or endorsed by hudl or any of these scouting apps.)

See also the [datavolley R package](https://github.com/raymondben/datavolley) for handling DataVolley files. The data structures and conventions used by `volleyxml` have been chosen to be similar to those of the `datavolley` package.

## Installation

```{r eval=FALSE}
library(devtools)
install_github("raymondben/volleyxml")
```

## Example

Read the example data file bundled with the package:
```{r}
library(volleyxml)
x <- vx_read(vx_example_file())
summary(x)
```
